Other metrics

### 2021-02-25 analysis/rev_prototyping/additional_metrics_results.Rmd
breadth indices

Working on a breadth index here (stuff needs to run).

@@

Working on the breadth index (stuff needs to run).

>>>>

Breadth index - note use of 2 tailed because of interest in low numbers of singletons for Gentry.

I haven't fully groked the breadth index, but I think...

- It declines with increasing size of the feasible set, but not as dramatically as the other indices.
- The Gentry region (low N/S tail on the right) is not remarkable for the size of the FS or the (2-tailed) breadth index, but has an extremely high median propotion of singletons.

ggplot(all_di, aes(nparts, nsingletons_95_ratio_2t, color = dat)) +
  geom_point(alpha = .3) +
  scale_x_log10()

# 
# ggplot(all_di, aes(s0, n0, color = nsingletons_95_ratio_2t)) +
#   geom_point(alpha = .3) +
#   scale_x_log10() +
#   scale_y_log10() +
#   scale_color_viridis_c()
# 
# 
# ggplot(all_di, aes(n0/s0, nsingletons_95_ratio_2t, color = dat)) +
#   geom_point(alpha = .3) +
#   scale_x_log10()
# 
# 
# ggplot(all_di, aes(n0/s0, nparts, color = dat)) +
#   geom_point(alpha = .3) +
#   scale_x_log10() +
#   scale_y_log10()

ggplot(all_di, aes(s0, n0, color = nsingletons_median / s0)) +
  geom_point(alpha = .3) +
  scale_x_log10() +
  scale_y_log10() +
  scale_color_viridis_c()

# 
# ggplot(all_di, aes(s0, n0, color = nsingletons / s0)) +
#   geom_point(alpha = .3) +
#   scale_x_log10() +
#   scale_y_log10() +
#   scale_color_viridis_c()

@@

ggplot(all_di, aes(nparts, shannon_95_ratio_2t, color = dat)) +
  geom_point(alpha = .3) +
  scale_x_log10()

ggplot(all_di, aes(nparts, shannon_95_ratio_2t, color = dat)) +
  geom_point(alpha = .3) +
  scale_x_log10() +
  xlim(0, 100000)

## 2 tailed breadth indices

ggplot(all_di, aes(nparts, shannon_95_ratio_2t, color = dat)) +
  geom_point(alpha = .3) +
  scale_x_log10()

ggplot(all_di, aes(nparts, skew_95_ratio_2t, color = dat)) +
  geom_point(alpha = .3) +
  scale_x_log10()

ggplot(all_di, aes(nparts, simpson_95_ratio_2t, color = dat)) +
  geom_point(alpha = .3) +
  scale_x_log10()

ggplot(all_di, aes(nparts, nsingletons_95_ratio_2t, color = dat)) +
  geom_point(alpha = .3) +
  scale_x_log10()
